### 2016-08-30 ReviewComments/meta.tex
revision comments

\response{In addition to the points in Response 2, another novelty of our work lies in the 
techniques. 
Although the idea of star-partition and apriori-partition are well-known, 
linking them together to solve the problem in trajectory domain has not been attempted before.
Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
anti-monotonicity) which have not been proposed before.
}

@@

\response { The evaluations are added in Table 7 and Figure 8. Due to the space limit, we only provide the summary of performance skew in Table 9 (i.e., the longest time-taking task vs stand deviation of each task). As per our analysis, the skew is limited because every stars are of similar sizes. The references of apriori and star partition are added accordingly in Section 5.1 and Section 5.2.
}

>>>>

\response{In addition to the points in Response 2, another novelty of our work lies in the 
techniques. 
Although the idea of star partition and apriori enumeration are well-known, 
linking them together to solve the problem in trajectory domain has not been attempted before.
Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
anti-monotonicity) which have not been previously proposed.
}

@@

\response { 
Similar responses with Response 6, 7 and 9.
}

### 2016-08-30 ReviewComments/review1.tex
revision comments

\response{
We agree with the reviewer that utilizing advanced Spark features
would benefit our solutions. In fact, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine). As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance. Using the DAG execution engine, we are able to adopt a Map-Planning-Reduce work flow. With the support of in-memory caching of RDDs,
the Map results need not to be recomputed after the planning phase. As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).  If without Spark's features, such an optimization would be hardly possible.

We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
%
%We are unsure about whether adapting other features in Spark (e.g., Spark streaming, Spark SQL, Spark Graph) would help to improve our solutions. Since they are solutions 
%%
%
%In this work, we do not include 
%these optimization in-depth because we set out focus 
%on solving the challenges in parallelizing the 
%GCMP mining algorithms.
%We are also in progress of open-sourcing a Spark-tailored
%version of SPARE.
}

>>>>

\response{
We agree with the reviewer that utilizing advanced Spark features
would benefit our solutions. Indeed, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine). As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance. Using the DAG execution engine, we are able to augment traditional Map-Reduce workflow to the Map-Planning-Reduce workflow. With the support of in-memory caching of RDDs,
the Map results need not to be recomputed after the planning phase. As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).  If without Spark's features, such an optimization would be hardly possible, but SPARE-RD is still more efficient than the baseline TRPM.

We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
}

### 2016-08-30 ReviewComments/review2.tex
revision comments

\response{
We admit that the gap parameter is also used in
mining Gap-restricted Sequential Patterns (GSP). However, the novelty
of this paper is not merely on introducing the gap-constraint to the
co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
for mining various co-movement patterns with flexible constraints. With
these constraints, users are able to define a more accurate pattern
which are free from the anomalies (e.g., loss-connection anomaly as in Figure 2).

Besides, the nature of GSP and GCMP are different. The goal of GSP 
is to find the sequences which conform to the gap constraint and occur frequently.
When counting the occurrence of a sequence in GSP, the object
which a sequence belongs to does not matter. Therefore, for
a pattern result in GSP, it cannot guarantee either the 
distinction of involved objects or the closeness of those objects.
In contrast, GCMP has requirements on both the spatial closeness 
of objects and the number of distinct objects.
Due to the unawareness of objects, techniques that are used in GSP 
cannot be directly applied on GCMP. We also summarize the difference
in Section 2.5.
%
%When counting the occurrence of a sequence, 
%the object the sequence belongs does not matter. 
%Therefore, a pattern in FS may corresponds to any objects where
%the closeness or distinction of objects are not statisfied. Due
%to this difference, FS solutions cannot be directly applied on GCMP.
%
%
%We agree with the reviewer that gap parameter is 
%also used in the Sequence Mining problem. However, 
%Sequence mining problem is different from the GCMP mining problem. 
%The major difference is that in sequence mining problem, the object
%itself is not considered. In particular, the frequency of a sequence is 
%counted as the occurrence of a sequence. Thus, an object may
%contribute multiple occurrence of a sequence. Conversely, GCMP
%in addition to impose the gap parameter in the temporal constraint, also 
%require the objects in the pattern to be close. Due to this difference,
%Sequence mining solutions cannot support GCMP mining.
%
%that the gap parameter is an old concept. 
%However, the novelty of GCMP lies in the unification and generalization of existing patterns which provide
%a one-stop solution for co-movement pattern detection. And the
%gap parameter merely is used for solving the loose-connection anomaly (as in Figure 2). 
%
%Moreover, the problem of Sequence mining is also different from Trajectory mining.
%The major difference is that sequence mining do not consider the distinction between
%objects and the closeness among objects. This makes the solutions in Sequence mining
%unable to be applied in GCMP. We summarize these points in Section 2.5 of the revised paper.
%
%We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
%modeling lies in unifying existing movement patterns in the trajectory domain. 
%The gap parameter is naturally introduced to 
%solve the loose-connection anomaly (as in Figure 2).
%%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
%In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
%and distinguish the sequential mining problem with our problem. 
}

@@

of SPARE, a pattern $c$ is outputted if non of its superset would become a valid pattern (Line 12-14).
This prohibits the output $c$ to be a subset of any patterns.
These mechanisms effectively condense the output size by subsuming smaller

@@

the number of potential patterns.

@@

\response{We agree that domain-specific constraints
on spatiotemporal mining could be similar to GCMP.
However, the domain-specific constraints (such as directions in road networks)
are nontrivial to be generalized. Since our GCMP model and technical solutions
do not leverage the domain knowledge, we can support
pattern discovery in broader scenarios such as user check-in history in social networks, visitor movements in a building and 
passenger flows in a city. We also add the discussion in Section 2.3.
}

>>>>

\response{
We admit that the gap parameter is also used in
mining Gap-restricted Sequential Patterns (GSP). However, the novelty
of this paper is not merely on introducing the gap-constraint to the generalized
co-movement pattern. Instead, we provide a one-stop solution (both in modeling and in technical)
for mining various co-movement patterns with flexible constraints. With
these constraints, users are able to define a more accurate pattern
which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).

Besides, the essence of GSP and GCMP are different. The goal of GSP 
is to find the sequences which conform to the gap constraint and occur frequently.
When counting the occurrence of a sequence in GSP, the object
which a sequence belongs to does not matter. Therefore, 
in a GSP result, the involved objects may be neither
 distinct nor close.
In contrast, GCMP imposes requirements on both the spatial closeness 
of objects and the number of distinct objects.
Due to the unawareness of objects, techniques that are used in GSP 
cannot be directly applied on GCMP. We summarize this difference
in Section 2.5.
%
%When counting the occurrence of a sequence, 
%the object the sequence belongs does not matter. 
%Therefore, a pattern in FS may corresponds to any objects where
%the closeness or distinction of objects are not statisfied. Due
%to this difference, FS solutions cannot be directly applied on GCMP.
%
%
%We agree with the reviewer that gap parameter is 
%also used in the Sequence Mining problem. However, 
%Sequence mining problem is different from the GCMP mining problem. 
%The major difference is that in sequence mining problem, the object
%itself is not considered. In particular, the frequency of a sequence is 
%counted as the occurrence of a sequence. Thus, an object may
%contribute multiple occurrence of a sequence. Conversely, GCMP
%in addition to impose the gap parameter in the temporal constraint, also 
%require the objects in the pattern to be close. Due to this difference,
%Sequence mining solutions cannot support GCMP mining.
%
%that the gap parameter is an old concept. 
%However, the novelty of GCMP lies in the unification and generalization of existing patterns which provide
%a one-stop solution for co-movement pattern detection. And the
%gap parameter merely is used for solving the loose-connection anomaly (as in Figure 2). 
%
%Moreover, the problem of Sequence mining is also different from Trajectory mining.
%The major difference is that sequence mining do not consider the distinction between
%objects and the closeness among objects. This makes the solutions in Sequence mining
%unable to be applied in GCMP. We summarize these points in Section 2.5 of the revised paper.
%
%We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
%modeling lies in unifying existing movement patterns in the trajectory domain. 
%The gap parameter is naturally introduced to 
%solve the loose-connection anomaly (as in Figure 2).
%%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
%In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
%and distinguish the sequential mining problem with our problem. 
}

@@

of SPARE, a pattern $c$ is outputted if none of its supersets could become a valid pattern (Line 12-14).
This ensures the output $c$ is not a subset of some pattern.
These mechanisms effectively condense the output by subsuming smaller

@@

the size of the output.

@@

\response{We understand that spatiotemporal mining with domain-constraints
looks similar to GCMP.
However, those techniques often heavily utilize the domain knowledge (such as
directions in road networks) which are nontrivial to be generalized.
Differently, since our GCMP model and technical solutions
do not leverage the domain knowledge, we can support
pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
passenger flows in a city. We also add the discussion in Section 2.3.
}

### 2016-08-30 ReviewComments/review3.tex
revision comments

\response{
We thank the reviewer for suggesting a better way of implementing 
the baseline algorithm (i.e., TRPM). However, this could
hardly be done after our investigations. The major reason is
that current version of Spark SQL (i.e., 1.6.2 released in June)
does not support the User Defined Aggregate Function (UDAF) on window
function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line sweep algorithm (Algorithm 1) using Spark SQL 
primitive aggregates (e.g., sum, avg, rank and nth-tile)
is beyond our abilities.

Further, we believe the performance boost on TRPM from Spark SQL
is very limited. The reason is that our 
Line Sweeping Mining algorithm (Algorithm 1) is not a 
properly reducible function. That is, the result of a 
smaller window could not be used to compute the result of a larger
window. In such a case, Spark SQL has to process each
window independently in parallel, which is equivalent to our TRPM implementation.
%We agree that leveraging more advanced Spark features
%could further improve the performance of our solutions. 
%We do not heavily leverage these features because 
%we wish to focus on designing parallel GCMP mining algorithms.
%%to provide a general parallel framework which does not tie to Spark.
%Nevertheless, we are in progress in developing
%a better open-sourced version with Spark-tailored optimization. 
%In the revision, we try to add a DataFrame based TRPM solution 
%which aims to leverage the window functions from Spark-SQL.
%However, to the best of our efforts, we could not achieve this goal in a short time. 
%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
%is nontrivial. Nonetheless, we expect less performance
%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
%properly reducible, where Spark system would fail to leverage the partial aggregates
%across multiple windows. As a result, it would be equivalent to our current TRPM
%solution where windows are processed independently in parallel.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

@@

\response{We add Table 7 to include vcore-seconds 
and RDD memory usage for both TRPM and SPARE. We also add a clear description on partitions in Section 6.
}

@@

\response{We complement Figure 8 with the breakdown cost of TRPM. This
comparison showcases the benefits of both Star Partition (in mapshufle phase)
and Apriori Enumeration (in reduce phase) of SPARE.
}

@@

\response{We thank the reviewer for the correction. We have changed many unprofessional terms.
}

@@

\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
}

>>>>

\response{
We thank the reviewer for suggesting a better way of implementing 
the baseline algorithm (i.e., TRPM). However, this could
hardly be done after our investigations. The major reason is
that the current version of Spark-SQL (i.e., 1.6.2 just released in June)
does not support the User Defined Aggregate Function (UDAF) on window
function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line Sweep algorithm (Algorithm 1) using Spark-SQL 
primitive aggregates (e.g., sum, avg, rank and nth-tile)
is beyond our abilities.

Further, we believe the performance boost on TRPM from Spark-SQL
is very limited. The reason is that our 
Line Sweep Mining algorithm (Algorithm 1) is not a 
properly reducible function. That is, the result of a 
smaller window could not be used to compute the result of a larger
window. In such a case, Spark-SQL has to process each
window independently in parallel, which is equivalent to our TRPM implementation.
%We agree that leveraging more advanced Spark features
%could further improve the performance of our solutions. 
%We do not heavily leverage these features because 
%we wish to focus on designing parallel GCMP mining algorithms.
%%to provide a general parallel framework which does not tie to Spark.
%Nevertheless, we are in progress in developing
%a better open-sourced version with Spark-tailored optimization. 
%In the revision, we try to add a DataFrame based TRPM solution 
%which aims to leverage the window functions from Spark-SQL.
%However, to the best of our efforts, we could not achieve this goal in a short time. 
%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
%is nontrivial. Nonetheless, we expect less performance
%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
%properly reducible, where Spark system would fail to leverage the partial aggregates
%across multiple windows. As a result, it would be equivalent to our current TRPM
%solution where windows are processed independently in parallel.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

@@

\response{In our implementation, we take a fixed 486 partitions (Section 6)
for each RDD. The partition number is determined based on 
the parallel tuning guide by Cloudera~\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}.
To study the load balance, we revise Section 6.2.2 by comparing TRPM, SPARE with random 
task allocation and SPARE with best-fit task allocation (Section 5.3). We present
the summary of the execution time for each method on longest job, shortest job and standard
deviation of all jobs in Table 9. As the table show, SPARE has a better load balance (low deviation)
than SPARE-RD which indicates the effectiveness of the best-fit strategy. Further, TRPM
generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition.
Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.

Next, we add Table 7 (Section 6.1) to compare
the resource usage (e.g., Vcore-seconds, Memory and Running Time) between SPARE and TRPM.
The table tells that both SPARE and TRPM are resource efficient.
In particular, the RDDs for both SPARE and TRPM only take less than 20\% of 
the available memory. This infers the potential of SPARE and TRPM in handling 
even larger trajectories with current system resources.
%
%include vcore-seconds 
%and RDD memory usage for both TRPM and SPARE. 
%As the table show, both TRPM and SPARE are resource efficient. 
%The maintained RDDs only takes less than 20\% of the entire memory. 
%We also add a clear description on partitions in Section 6.
}

@@

\response{We complement Figure 8 (Section 6.1) by including the breakdown cost of TRPM. 
In SPARE, star partition takes place in the Map-Shuffle phase while
Apriori enumeration takes place in the Reduce phase. As shown in the
new Figure 8, both star partition and apriori enumeration contribute to 
the final performance gain of SPARE. In particular, in the Map-Shuffle phase,
SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
less data are transformed and shuffled in the star partition.
In the Reduce phase, SPARE saves 46\%-81\% time as compared to TRPM. This confirms 
the efficiency of our Apriori enumerator with various optimization (e.g., sequence simplification,
anti-monotonicity and forward closure checking).
}

@@

\response{We thank the reviewer for the correction. We have changed these unprofessional terms.
}

@@

\response{ We use all cores in the single node to conduct the experiment. We revise the description in Section 6.2.3.
}

### 2016-08-30 sec6_experiment.tex
revision comments

\revised{
\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken by TRPM and SPARE under the default setting. Both TRPM and SPARE are resource efficient as they only occupy less than 20\% 
of the available memory which reveals their potential to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues
to the set of effective pruning procedures.

\begin{table}[h]
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ \cline{2-5} 
                                       & SPARE           & 334                               & 47,430                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ \cline{2-5} 
                                       & SPARE           & 480                               & 49,835                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ \cline{2-5} 
                                       & SPARE           & 812                               & 89,390                 & 35,912               \\ \hline
\end{tabular}
\caption{Resources taken for TRPM and SPARE. Time is in seconds representing observed performance. Vcore-seconds is the aggregate of time spent in each core. Memory is in MB representing the actual size of RDDs.}
\label{tbl:resource}
\end{table}
}
%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

@@

\begin{table}[h]
\centering \small
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time (in seconds) among executors.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD \revised{with TRPM as comparison}. We observe that the map and shuffle time of SPARE and SPARE-RD are identical . The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). \revised{We further observe that TRPM takes more time in each phase, which confirms the efficiency of Star Partition and Apriori Enumeration.} We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

>>>>

\revised{
\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken 
by TRPM and SPARE under the default setting. Both TRPM and SPARE are 
resource efficient as they only occupy less than 20\% 
of the available memory (i.e., 270GB) . Again, SPARE outperforms TRPM in both the execution time and the memory usage.

%The result also reveals the potential of the two solutions to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues to the set of effective pruning procedures.

\begin{table}[h]
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ %\cline{2-5} 
                                       & SPARE           & 237                               & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ %\cline{2-5} 
                                       & SPARE           & 341                               & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ %\cline{2-5} 
                                       & SPARE           & 580                               & 68,580                & 35,912               \\ \hline
\end{tabular}
\caption{Resources taken for TRPM and SPARE. Time is in seconds representing observed performance. Vcore-seconds is the aggregate of time spent in each core. Memory is in MB representing the actual size of RDDs.}
\label{tbl:resource}
\end{table}
}
%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

@@

\begin{table}[h]
\centering \small
%\begin{tabular}{|c|c|c|c|c|}
%\hline
%\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
%                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
%Shopping                 & 295              & 41         & 237             & 21       \\ \hline
%GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
%Taxi                     & 681              & 147        & 580             & 96       \\ \hline
%\end{tabular}
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
\multirow{3}{*}{Shopping}              & TRPM            &     426                          & 597                 & 35 
\\ %\cline{2-5} 
                                       & SPARE-RD          & 122                               &  295             & 41
\\% \cline{2-5}                                        
									   & SPARE           &  134                              &   237               & 21
\\ \hline                                
\multirow{3}{*}{GeoLife}              & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
                                       & SPARE-RD          &  38                               &   484               & 148
\\ %\cline{2-5}                                        
									   & SPARE           &   107                             &     341             & 96
\\ \hline
\multirow{3}{*}{Taxi}              & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
                                       & SPARE-RD          & 122                               & 681                 & 109
\\ %\cline{2-5}                                        
									   & SPARE           &   134                             &  580                & 56               
\\ \hline
\end{tabular}
  \caption{Statistics of execution time (in seconds) among all executors.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages 
for SPARE and SPARE-RD \revised{with TRPM as comparison}. We observe that the map and shuffle time of SPARE and SPARE-RD are identical . The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). 
\revised{Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
efficiency of the star partition and apriori enumeration.} 
\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}. As the table shows, SPARE produces more balanced jobs
than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
However, TRPM still takes much longer time than SPARE algorithms.}
%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
%We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
